The Evolution of Phenotypically Invariant Genetic Networks

### 2021-08-12 review-responses2.tex

\vskip 2em

\noindent
{\bf To the Editor(s) -- }

\vskip 1em

We are writing to submit a revision of our manuscript, ``{System drift and speciation}'' (ID 21-0262), for your review.
We would like to thank you and the reviewers for your enthusiasm
and your suggestions -- they have helped us improve our manuscript's accuracy and clarity.

### 2021-08-12 kalman_walk_paper.tex
recomb clarification

First, we must specify how sexual reproduction acts on these systems.
Suppose that each of a diploid organisms' two genomes encodes a set of system coefficients
with the same kryptotype dimension. 
We assume that a diploid which has inherited systems $(A', B', C')$ and $(A'', B'', C'')$ from its two parents
has phenotype determined by the system that averages these two,
$((A'+A'')/2, (B'+B'')/2, (C'+C'')/2)$.
(We do not, however, specify a model for recombination to produce the inherited systems,
as the details will depend on the genetic basis of the system coefficients;
two extremes are depicted in the two panels of Figure~\ref{fig:conceptual_fig}.) \revpoint{2}{6}

\jss{Could add something like this?}

In Example \ref{ex:hybrid_osc} and Figure \ref{fig:hybs}, however, meiosis is modeled such that it recombines system coefficients independently,
to form haploid gametes. E.g., a possible oscillator gamete could be formed by shuffling the diploid's haploid genomes -- with one genome's coefficients notated with Greek and the other with Latin, as follows,
$\left[ \begin{smallmatrix} \alpha & \beta \\ \gamma & \delta \end{smallmatrix} \right] \times \left[ \begin{smallmatrix} a & b \\ c & d \end{smallmatrix} \right] \to \left[ \begin{smallmatrix} \alpha & b \\ c & \delta \end{smallmatrix} \right]$.

>>>>

First, we must specify how sexual reproduction acts on these systems.
Suppose that each of a diploid organisms' two genomes encodes a set of system coefficients
with the same kryptotype dimension. 
We assume that a diploid which has inherited systems $(A', B', C')$ and $(A'', B'', C'')$ from its two parents
has phenotype determined by the system that averages these two,
$((A'+A'')/2, (B'+B'')/2, (C'+C'')/2)$.
In general, how parental systems are recombined and inherited
depends on the genetic architecture of the segregating variation.
\revpoint{2}{6}
For the purposes of examples in this paper
(Example \ref{ex:hybrid_osc} and Figure \ref{fig:hybs}),
we take the simplest assumption that each system coefficient is encoded by a nonrecombining locus,
and that these loci are unlinked.
For instance, if
one genome's coefficients are written with Greek and the other with Latin,
a possible oscillator gamete might be produced as follows:
$\left[ \begin{smallmatrix} \alpha & \beta \\ \gamma & \delta \end{smallmatrix} \right] \times \left[ \begin{smallmatrix} a & b \\ c & d \end{smallmatrix} \right] \to \left[ \begin{smallmatrix} \alpha & b \\ c & \delta \end{smallmatrix} \right]$.
